An overview of the oolong package.

### 2020-02-24 vig_body.Rmd
Add a Makefile to generate the documentation. ref #16

---
title: "An overview of the oolong package."
output: github_document
author:
  - Chung-hong Chan ^[University of Mannheim]
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
  )
set.seed(42)
```
The validation test is called "oolong test" (for reading tea leaves). Creating oolong test for topic models and dictionary-based uses the same function: `create_oolong()`. The most important parameters are `input_model` and `input_corpus`. Setting each of them to `NULL` generates different tests.

>>>>

The validation test is called "oolong test" (for reading tea leaves). Creating oolong test for topic models and dictionary-based uses the same function: `create_oolong()`. The most important parameters are `input_model` and `input_corpus`. Setting each of them to `NULL` generates different tests.
